\section{Otherworldy Patrons}

\subsection{Slaad \cite{slaad-patron}}
{Your patron is a slaad lord, the most powerful of grotesque creatures formed from pure chaos and horrific reproductive cycles. Its motives are to sow discord and bring down the laws of man and, if possible, nature itself. Slaad lords powerful enough to grant pacts include Chourst, Lord of Randomness; Rennbuu, Lord of Colors; Ssendam, Lord of Madness; Ygori, Lord of Entropy; and other chaotic beings.}

\subsubsection{Expanded Spell List}
{Your Slaad patron lets you choose from an expanded list of spells when you learn a warlock spell. The following spells are added to the warlock spell list for you.}

\header{Slaad Expanded Spells}
\begin{spelltable}
	\textbf{Spell Level}  & \textbf{Spells} \\
	1st & \textit{Tasha's Hideous Laughter, Grease} \\
	2nd & \textit{Detect Thoughts, Alter Self} \\
	3rd & \textit{Stinking Cloud, Slow} \\
	4th & \textit{Polymorph, Compulsion} \\
	5th & \textit{Mislead, Modify Memory} \\
\end{spelltable}

\subsubsection{Chaotic Body and Mind}
Starting at 1st level, you are able to use a bonus action to transform your fists into fearsome claws. You are proficient in using your claws, and you can use your claws to make an unarmed attack inflicting d4 slashing damage. The damage increases one die level at the 5th and 11th warlock level. If you choose \textit{Pact of the Blade}, your claws are now considered magical for the purposes of overcoming resistance and immunity to nonmagical attacks and damage. Your claws are also considered a pact weapon for the purposes of working with the relevant blade pact invocations.

Your exposure to the slaadi mind and language has allowed you to understand and speak Slaadi. You are able to communicate telepathically with slaadi up to 30 feet.

\subsubsection{Slaadi Skin}
Starting at Level 6, you have learned to harness the chaotic energy provided by your patron to acquire the Slaadi's thick skin. When a creature casts a spell at you, you can use your reaction to receive advantage on the spell saving throw or magical effect. This can be used once every long rest. When you aren't wearing armor, your AC equals 13 + your DEX modifier.

You may choose to adopt the skin tones of the slaad. At level 6, your skin has a very faint green color. At level 10, your skin takes on an ashy gray color. At level 14, your skin has a faint, light black color.

\subsubsection{Sow Discord}
Starting at Level 10, you revel in causing chaos in battle and befuddling your enemies. You learn the \textit{confusion} spell if you do not already know it, and it does not count towards your spells known. You can cast \textit{confusion} once without expending one of your spell slots. This feature can only be used once every long rest.

\subsubsection{Seeds of Chaos}
Starting at Level 14, on a successful unarmed attack or scraping of the skin with your claws on an incapacitated humanoid, you can choose to infect him with a disease called the chaos phage. The humanoid must make a Constitution saving throw against your spell save DC or become diseased. On a successful save, nothing happens to the humanoid. On a failed save, within 2d12 hours, the person will die as a slaadi tadpole bursts out of the humanoid's insides. The tadpole will transform into a red or blue slaad in 2d12 hours. If the humanoid dies before full incubation, the tadpole will not survive but the body remains a potential source of infection for 24 hours. The phage can be spread if exposed to the diseased humanoid's blood.

Every time you use this feature, you tap into the slaad's regenerative nature and recover health equivalent to your warlock level times 3, allowing you to sustain your spread of mayhem. You can recover health regardless of whether the disease successfully took hold. This feature can only be used once every long rest.

\subsection{Slaad Tadpoles \cite{tadpole}}
Slaad tadpoles are the larval form shared in common by all slaad subspecies. Resembling not a mundane tadpole but a fanged frog’s head with a finned tail where its neck should be, these belligerent little creatures swim the tides of chaos everywhere in the Maelstrom. The raw chaos of their bodies is not yet fully coalesced, making them highly elusive.

Slaad tadpoles come into being in countless ways: some spawned through sexual reproduction, some implanted in victims in the form of a deadly virus called “chaos phage” that slowly takes over a host body, and so on. A slaad tadpole matures into an adult slaad in a period of days, months, or even years, the amount of time seemingly random.

% You can optionally not include the background by saying
% begin{monsterboxnobg}
\begin{monsterbox}{Slaad Tadpole}
	\textit{CN Tiny outsider (chaotic, extraplanar, slaad)}\\
	\hline
	\basics[%
	armorclass = 14,
	hitpoints  = 26,
	speed      = 10 ft
	]
	\hline
	\stats[
	STR = \stat{13}, % This stat command will autocomplete the modifier for you
	DEX = \stat{14},
	CON = \stat{12},
	INT = \stat{3},
	WIS = \stat{10},
	CHA = \stat{11}
	]
	\hline
	\details[%
	% If you want to use commas in these sections, enclose the
	% description in braces.
	% I’m so sorry.
	senses = {Darkvision 60 ft., Perception +7},
	languages = {Slaad},
	damageimmunities = {Sonic},
	damageresistances = {Acid, Cold, Elecricity, Fire},
	conditionimmunities = {Charmed},
	challenge = 2
	]
	\hline \\[1mm]
	\begin{monsteraction}[Monster-super-powers]
		This Monster has some serious superpowers!
	\end{monsteraction}
	\monstersection{Actions}
	\begin{monsteraction}[Chaos Shift (Su)]
		Once per turn, when attacked in melee, a slaad tadpole can instantly teleport 10 ft. away in a random direction, avoiding damage.
	\end{monsteraction}

	\begin{monsteraction}[Fade (Su)]
	When a slaad tadpole deals damage, it becomes incorporeal until the start of its next turn.
	\end{monsteraction}
\end{monsterbox}
